Syntax and Semantics of Abstract Binding Trees

### 2015-12-22 paper.tex
Shorten arrows from tikz-pfeile
fix renaming notation
remove bureaucratic corporatespeak

\usepackage{appendix}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{tikzpfeile}
\usepackage{todonotes}
\usepackage{url}

@@

Declaring a new assignable consists in providing an initial value, and an
expression binding a symbol (which shall represent the assignable in scope).
Note that the functoriality of $\Operators$ guarantees for any renaming
$\Of{\varrho}{\Upsilon\inj\Upsilon'}$, a family of lifted maps
$\Of{\Operators_a(\varrho)}{\Operators_a(\Upsilon)\inj\Operators_a(\Upsilon')}$
natural in $a$, such that
$\IsOperator{\Upsilon'}{\Operators(\varrho)(\vartheta)}{a}$ when
$\IsOperator{\Upsilon}{\vartheta}{a}$. In particular, the renaming
$\Upsilon,u\mapsto\Upsilon,v$ shall take $\mathtt{get}[u]$ to
$\mathtt{get}[v]$. Going forward, we will write $\vartheta\varrho$ for
$\Operators_a(\varrho)(\vartheta)$.

@@

\begin{gather*}
  \infer[\textit{var}]{
    \IsRenaming{\varrho}{x}{x}
  }{
  }
\\[6pt]
  \infer[\textit{mvar}]{
    \IsRenaming{\varrho}{
      \MApp{\MV{m}}{\vec{u}}{M_0,\dots,M_n}
    }{
      \MApp{\MV{m}}{\vec{v}}{N_0,\dots,N_n}
    }
  }{
    \Match{\varrho(\vec{u})}{\vec{v}}
&
    \HypJ{
      \IsRenaming{\varrho}{M_i}{N_i}
    }{
      \Leq{i}{n}
    }
  }
\\[6pt]
  \infer[\textit{app}]{
    \IsRenaming{\varrho}{
      \App{\vartheta}{E_0,\dots,E_n}
    }{
      \App{\vartheta\varrho}{F_0,\dots,F_n}
    }
  }{
    \HypJ{
      \IsRenaming{\varrho}{E_i}{F_i}
    }{
      \Leq{i}{n}
    }
  }
\\[6pt]
  \infer[\textit{abs}]{
    \IsRenaming{\varrho}{
      \MkBTm{\vec{u}}{\vec{x}}{M}
    }{
      \MkBTm{\vec{u}}{\vec{x}}{N}
    }
  }{
    \IsRenaming{\varrho\setminus\vec{u}}{M}{N}
  }
\end{gather*}

@@

Going forward, we will write $\Subst{N}{x}{M}$ for $M'$ when
$\IsSubst{N}{x}{M}{M'}$, and $\Subst{\vec{N}}{\vec{x}}{M}$ for the simultaneous
substitution of $\vec{N}$ for $\vec{x}$ in $M$.

>>>>

\usepackage{appendix}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{agda} % this should come after ams*
\usepackage{catchfilebetweentags}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{ifdraft}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{setspace}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage[length=.5]{tikzpfeile}
\usepackage{todonotes}
\usepackage{url}

@@

Declaring a new assignable consists in providing an initial value, and an
expression binding a symbol (which shall represent the assignable in scope).
Note that the functoriality of $\Operators$ guarantees for any renaming
$\Of{\varrho}{\Upsilon\inj\Upsilon'}$, a family of lifted maps
$\Of{\Operators_a(\varrho)}{\Operators_a(\Upsilon)\inj\Operators_a(\Upsilon')}$
natural in $a$, such that
$\IsOperator{\Upsilon'}{\Operators(\varrho)(\vartheta)}{a}$ when
$\IsOperator{\Upsilon}{\vartheta}{a}$. In particular, the renaming
$\Upsilon,u\mapsto\Upsilon,v$ shall take $\mathtt{get}[u]$ to
$\mathtt{get}[v]$. In the future, we will write $\Rename{\varrho}{\vartheta}$
for $\Operators_a(\varrho)(\vartheta)$.

@@

\begin{gather*}
  \infer[\textit{var}]{
    \IsRenaming{\varrho}{x}{x}
  }{
  }
\\[6pt]
  \infer[\textit{mvar}]{
    \IsRenaming{\varrho}{
      \MApp{\MV{m}}{\vec{u}}{M_0,\dots,M_n}
    }{
      \MApp{\MV{m}}{\vec{v}}{N_0,\dots,N_n}
    }
  }{
    \Match{\varrho(\vec{u})}{\vec{v}}
&
    \HypJ{
      \IsRenaming{\varrho}{M_i}{N_i}
    }{
      \Leq{i}{n}
    }
  }
\\[6pt]
  \infer[\textit{app}]{
    \IsRenaming{\varrho}{
      \App{\vartheta}{E_0,\dots,E_n}
    }{
      \App{\Rename{\varrho}{\vartheta}}{F_0,\dots,F_n}
    }
  }{
    \HypJ{
      \IsRenaming{\varrho}{E_i}{F_i}
    }{
      \Leq{i}{n}
    }
  }
\\[6pt]
  \infer[\textit{abs}]{
    \IsRenaming{\varrho}{
      \MkBTm{\vec{u}}{\vec{x}}{M}
    }{
      \MkBTm{\vec{u}}{\vec{x}}{N}
    }
  }{
    \IsRenaming{\varrho\setminus\vec{u}}{M}{N}
  }
\end{gather*}

@@

In the remainder, we will write $\Subst{N}{x}{M}$ for $M'$ when
$\IsSubst{N}{x}{M}{M'}$, and $\Subst{\vec{N}}{\vec{x}}{M}$ for the simultaneous
substitution of $\vec{N}$ for $\vec{x}$ in $M$.
